Stochastic Variance-Reduced Policy Gradient

### 2018-02-09 svrpg.tex
typo

\begin{abstract}
        In this paper, we propose a novel reinforcement-learning algorithm consisting in a stochastic variance-reduced version of policy gradient for solving Markov Decision Processes (MDPs).
        Stochastic variance-reduced gradient (SVRG) methods have proven to be very successful in supervised learning.
        However, their adaptation to policy gradient is not straightforward and needs to account for I) a non-concave objective function; II) approximations in the full gradient computation; and III) a non-stationary sampling process.
        The result is SVRPG, a stochastic variance-reduced policy gradient algorithm that leverages on importance weight to preserve the unbiasedness of the gradient estimate.
        Under standard assumptions on the MDP, we provide convergence guarantees for SVRPG with a convergence rate that is linear under increasing batch sizes.
        Finally, we suggest practical variants of SVRPG, and we empirically evaluate them on continuous MDPs.
\end{abstract}

@@

>>>>

\begin{abstract}
        In this paper, we propose a novel reinforcement-learning algorithm consisting in a stochastic variance-reduced version of policy gradient for solving Markov Decision Processes (MDPs).
        Stochastic variance-reduced gradient (SVRG) methods have proven to be very successful in supervised learning.
        However, their adaptation to policy gradient is not straightforward and needs to account for I) a non-concave objective function; II) approximations in the full gradient computation; and III) a non-stationary sampling process.
        The result is SVRPG, a stochastic variance-reduced policy gradient algorithm that leverages on importance weights to preserve the unbiasedness of the gradient estimate.
        Under standard assumptions on the MDP, we provide convergence guarantees for SVRPG with a convergence rate that is linear under increasing batch sizes.
        Finally, we suggest practical variants of SVRPG, and we empirically evaluate them on continuous MDPs.
\end{abstract}

@@

\paragraph{Videos:} The supplementary materials include videos showing the behavior of the final SVRPG policies on the three considered tasks.
